QALY Comparisons - `r params$experiment` - `r params$intervention` - `r params$baseline`

### 2024-03-05 minos/outcomes/QALY_comparison2.Rmd
Small tweaks and better reporting of large values (formatted with commas)

```{r}
experiment <- params$experiment
baseline <- params$base
intervention <- params$intervention
# 
# experiment <- 'default_config'
# baseline <- 'baseline'
# intervention <- '100All'
```

@@

>>>>

```{r}
# experiment <- params$experiment
# baseline <- params$base
# intervention <- params$intervention
# 
experiment <- 'default_config'
baseline <- 'baseline'
intervention <- '50All'
```

@@

print(paste("There are", sum(is.na(combined.pop.boosted$pop_boosted)), "NA pop_boosted values in combined.pop.boosted.", sep = ' '))
